Scholten Read Sanborn

### 2015-11-16 shinyapps/scholtenReadSanborn2014.Rmd
Update with interval model and paper introduction

>>>>

## Tradeoff model

attribute-based evaluation rule, in which the outcome advantage of one
option is weighted against the time advantage of the other, and the option with the great- est advantage is chosen.

These advantages are differences between weighted delays, w(tL) ? w(tS), or the effective interval (as in the interval discounting model), and differences between valued outcomes,
$v(x_L) - v(x_S)$ for $x_L > x_S > 0$ and $v(x_S) - v(x_L)$ for $x_L < x_S < 0$, or the effective compensation. The effective interval and the effective compensation are weighted against one another by a tradeoff function Q.

$$\begin{equation}
 Q(w(t_L) - w(t_S)) = 
    \begin{cases}
      v(x_L) - v(x_S), & \text{if}\ x_L > x_S > 0 \\
      v(x_S) - v(x_L), & \text{if}\ 0 > x_S > x_L
    \end{cases}
  \end{equation}$$

Analogous to the time-weighing function, the trade- off model has a normalized logarithmic value function:

$$\begin{equation}
 v(x) = 
    \begin{cases}
      \frac{1}{\gamma}\log(1+\gamma x), & \text{if}\ x > 0 \\
      -\frac{\lambda}{\gamma}  \log(1+\gamma (-x)), & \text{if}\ x < 0
    \end{cases}
  \end{equation}$$

where $\gamma > 0$ is diminishing absolute sensitivity to outcomes. Like the normalized expo- nential value function discussed by K
obberling and Wakker (2005), the value function in
Eq. 10 approaches constant sensitivity (unit elasticity) as $\gamma$ goes to 0 (linear value func- tion), approaches insensitivity (zero elasticity) as $\gamma$ goes to infinity (zero value function), and is decreasingly elastic otherwise, spanning the entire range from unit elasticity (as x goes to 0) to zero elasticity (as x goes to infinity)

```{r}
to_val_fn <- function(x, gamma, lambda) {
  x <- as.numeric(x)
  gamma <- as.numeric(gamma)
  lambda <- as.numeric(lambda)

  ifelse(x >= 0, 
         (1/gamma) * log(1 + gamma * x),
         -(lambda/gamma) * log(1+gamma*(-x)))
}

```{r}
inputPanel(
  sliderInput("gamma_to", "gamma diminishing absolute sensitivity to outcomes",  min=.01, max = .99, step=.001, value= .1),
  sliderInput("lambda_to", "Lambda loss aversion", value = 1,  min=1, max = 4, step = .05)
)

renderPlot({
  to_val_df <- data.frame(x = -100:100)
  to_val_df$lambda <- input$lambda_to
  to_val_df$gamma <- input$gamma_to

  to_val_df <- mutate(to_val_df, value = to_val_fn(x, gamma, lambda))

  ggplot(to_val_df, aes(x = x, y = value, group = 1)) +
    geom_line() +
    geom_abline(intercept = 0, slope=0) +
    geom_vline(xintercept = 0) +
    xlab("Outcome") +
    ylab("Value") +
    xlim(c(-100, 100))
})
```

The tradeoff fucntion weighs effective intervals against effective compensations

$$Q(t_S, t_L) = \frac{\kappa}{\alpha} \log
\left(1 + \alpha \left(\frac{w(t_L) - w(t_S)}{\vartheta}\right)^{\vartheta}\right)$$
